Tree establishment in models of forest dynamics: a key priority for further research

### 2023-02-16 manuscript/manuscriptRW.Rmd
added information on the missing site from LPJ-guess

Three models did not provide results from all the simulated samples or
sites to avoid unrealistic results, as follows. In the model 4C, a
threshold of a maximum basal area of 90 $m^2 ha^{-1}$ was used to avoid
unrealistic stand basal area data, and therefore not all the samples and
sites were reported. The reason for this is that 4C is not suitable for
long-term simulations without management, due to misrepresentations in
density-dependent mortality processes in long-term simulations and
assumptions of tree geometry that lead to unrealistic single tree
dimensions of very old individuals. LPJ-GUESS had 2% of the sample
outputs as grasslands that were considered in the data as zero stand
basal area and zero ingrowth for all the tree species simulated and one
site was not simulated.

>>>>

Three models did not provide results from all the simulated samples or
sites to avoid unrealistic results, as follows. In the model 4C, a
threshold of a maximum basal area of 90 $m^2 ha^{-1}$ was used to avoid
unrealistic stand basal area data, and therefore not all the samples and
sites were reported. The reason for this is that 4C is not suitable for
long-term simulations without management, due to misrepresentations in
density-dependent mortality processes in long-term simulations and
assumptions of tree geometry that lead to unrealistic single tree
dimensions of very old individuals. LPJ-GUESS had 2% of the sample
outputs without tree establishment and were considered in the data as
zero stand basal area and zero ingrowth for all the tree species
simulated and one site produced grasslands and was not included in the
results.
